---
title: "R Table Package Testing"
format: pdf
keep-tex: true
---

# Compatability of tables produced from R packages and quarto-->pandoc-->latex conversions

Comparisons of the translated tables created from the following R packages in a quarto doc:
- `gt`
- `kableExtra`
- `flextable`

We know that `kableExtra` has functions to format a table to latex, but I am not
sure the table that is visualized in an R chunk gets translated the same. We also
know that `flextable` tables rendered in a quarto doc can not be tagged and contain
misc. extra formatting (according to Gemini). The formatting from `flextable` is 
also very difficult to manually read and debug.

I know nothing of `gt` tables.

## Testing

Example data: tidyr::table2

```{r}
#| echo: false
exdat <- tidyr::table2
```

### Make tables from example data (unformatted)

#### `gt`

```{r}
#| echo: false
#| tbl-cap: Table produced from gt R package.
gt::gt(exdat)
```


#### `kableExtra`

```{r}
#| echo: false
#| tbl-cap: Table produced from kableExtra::kable.
kableExtra::kable(exdat)
```

```{r}
#| echo: false
#| tbl-cap: Table produced from kableExtra::kbl.
kableExtra::kbl(exdat)
```


#### `flextable`

```{r}
#| echo: false
#| tbl-cap: Table produced from flextable.
flextable::flextable(exdat)
```

**Note:** On first render, the tables are placed out of order and in random sections.

## Results


## Efforts for a solution


**Final Note:**


